---
output:
  pdf_document: default
  html_document: default
---
# Question 1

```{r}
x = c(5.6,6.3,7,7.7,8.4) 
y = c(8.8, 12.4, 14.8, 18.2, 20.8)
fit <- lm(y ~ x)
print(fit$coefficients)
```

Equation for the regression line for the given points is:
$y = 4.26x + -14.80 $

# Question 2

```{r}
f <- expression(24*x - 6*x*y^2 - 8*y^3)
dx <- D(f, 'x')
dy <- D(f, 'y')
## I calculated our critical values by setting our dx and dy equations to 0.
#cv = (-4, 2), (4, -2)
## Now we calculate our second derivatives.
d2x <- D(dx, 'x')
d2y <- D(dy, 'y')
dxy <- D(dx, 'y')
## We evaluate our second derivatives using our critical values.
x <- -4
y <- 2
a1 <- eval(d2x)
b1 <- eval(d2y)
c1 <- eval(dxy)
x <- 4
y <- -2
a2 <- eval(d2x)
b2 <- eval(d2y)
c2 <- eval(dxy)
## We evaluate our second derivative test using a, b, and c to get our value dtest at our critical point (-4, 2).
dtest1 <- (a1*b1) - (c1^2)
dtest2 <- (a2*b2) - (c2^2)
## Our value for dtest is less than 0 for each point so we have found two saddle points (-4, 2) and (4, -2).
```

Our value for dtest is less than 0 for each point so we have found two <b> saddle points (-4, 2) and (4, -2). </b>

# Question 3

Let Qh and Qn be the amount of sold units for house and name brand respectively.

$Qh = 81-21x+17y $
$Qn = 40+11x-23y $

Let Ph and Pn be the price for house and name brand respecively.

$Ph = x $
$Pn = y $

$R(x, y) = (Qh*Ph) + (Qn*Pn) $

$R(x, y) = (81x-21x^2+17yx) + (40y+11xy-23y^2) $

If house brand sells for <b>`$2.30`</b> and name brand for <b>`$4.10`</b>

```{r}
x <- 2.30
y <- 4.10
(81*x-21*x^2+17*y*x) + (40*y+11*x*y-23*y^2)
```

The revenue will be <b>$116.62</b>.

```{r}
# x + y = 96 so we know y = 96 - x
# We take the derivative of C(x,y) in respect to x after substituting y in terms of x:
C <- expression((1/6)*x^2 + (1/6)*(96 - x)^2 + 7*x + 25*(96 - x) + 700)
dx <- D(C, 'x')
# Using our formula dx we find x is equal to 75 when the slope is 0 so y is equal to 21.
```
The most cost effective approach is <b> x = 75, y = 21 </b>.

```{r}
library(pracma)

f <- function(x,y) exp(8*x+3*y) 
ans <- integral2(f, 2, 4, 2, 4, reltol = 1e-10)
```
